 

### 2021-01-25 vertical-thermal-review.Rmd
Update vertical-thermal-review.Rmd

>>>>

Related to something in the NSC paragraph:
In this section we could perhaps also consider differences in biomass distribution between canopy trees an understory plants, and what that may mean for performance at high temperature. What I'm thinking is the temperature sensitivity of respiration that applies to leaves, stems, and roots, and even though thermal acclimation of leaf respiration is common, much less is known about acclimation of stem and root respiration, and incomplete acclimation still increases the respiration load at higher temperature. It is possible that an increased respiration load is more disadvantageous for understory plants because 1), I suspect that a greater fraction of their total biomass is life biomass that respires (as opposed dead heartwood in the stems of big trees), and 2), because they operate closer to their light compensation point, so if they lose more carbon in respiration, they would need  to make up for lost carbon in photosynthesis, but might lack sunlight to do so
